### 2014-04-28 latex/phd_thesis.tex
Finished description of DSS. Described MOABS and DMAP. Describe inference framework and simulation model in Lacey et al. Need to fix - LaTeX doesn't compile

@@

bp & base pair \\
kb & kilobase = $1000$ bp \\
Mb & megabase = $1,000,000$ bp \\
Gb & gigabase = $1,000,000,000$ bp \\
WGBS & whole genome bisulfite sequencing \\
RRBS & reduced representation bisulfite sequencing \\
FDR & false discovery rate \\
DMR & differentially methylated region \\
DMC & differentially methylated cytosine \\

>>>>

% TODO: Remove all unused macros

@@

bp & base pair \\
kb & kilobase = $1000$ bp \\
Mb & megabase = $1,000,000$ bp \\
Gb & gigabase = $1,000,000,000$ bp \\
WGBS & whole genome bisulfite sequencing \\
RRBS & reduced representation bisulfite sequencing \\
FDR & false discovery rate \\
DMR & differentially methylated region \\
DMC & differentially methylated cytosine \\
HMM & hidden Markov model \\
CNV & copy number variant \\
